---
title: "Homework 1"
author: Natalie Boychuk 
output: github_document
---

This is my solution to Homework 1. 

_First I am going to load the packages I need._

```{r loading the tidyverse}
library(tidyverse)
```

## Problem 1
_Then I created a data frame with the specified elements_

```{r creating the dataframe}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a","b","c","d","e","f","g","h","i","j"),
    factor_vec = factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
  )
```

_I then took the mean of each variable in my data frame._ 

```{r attempting to take the mean}
    mean(pull(prob1_df, samp))
    mean(pull(prob1_df, samp_gt_0))
    mean(pull(prob1_df, char_vec))
    mean(pull(prob1_df, factor_vec))
```

After running this code I see cannot take the mean of the character vector or the factor vector, because R does not recognize these as numbers.

```{r results=FALSE}
    as.numeric(pull(prob1_df,samp_gt_0)) 
    as.numeric(pull(prob1_df,char_vec))
    as.numeric(pull(prob1_df,factor_vec))
```

I can convert the logical and factor vectors to numeric but I can't do the same thing with character vectors. I couldn't take the factor vector as a mean, but if I want to, I can convert this into a numeric vector and then take the mean. I can't do this with a character vector - this may be because R can't find a way to meaningfully assign numbers to characters. 

```{r converting logical vector and multiplying }
    as.numeric(pull(prob1_df,samp_gt_0))*pull(prob1_df,samp)
    as.factor(pull(prob1_df,samp_gt_0))*pull(prob1_df,samp)
    as.numeric(as.factor(pull(prob1_df,samp_gt_0)))*pull(prob1_df,samp)
```

## Problem 2 
_First, I loaded the penguin dataset_
```{r loading penguin dataframe}
data("penguins", package = "palmerpenguins")
```

The _Penguins_ dataset has `r nrow(penguins)` observations represented by rows and `r ncol(penguins)` variables (species, island, sex, bill length, bill depth, flipper length, year, and body mass in grams), which are displayed in the columns. Data was collected between 2007 and 2009. There are three species of penguin included in this study: Adelie (49.12.%),   Gentoo (36.05%), and Chinstrap (19.77%). The study was conducted over three islands: the Bisco, Dream, and Torgersen islands. Almost half of penguins (48.84%) were sampled on Biscoe Island, while slightly more than two-thirds (36.05%) were on Dream Island.

An average penguin in this dataset has a flipper that is 200.92mm long. Their bills are, on average, 43.92mm long and 17.15mm deep. The mean weight of penguins included in this study is 4201.75 grams. Nearly equal proportions of penguins were male (48.83%) and female (47.97%)  while 11 observations were missing data on gender. 


```{r getting descriptive variables}

##Variable names
variable.names(penguins)

##Year 
min(pull(penguins,year))
max(pull(penguins,year))

##Species 
levels(pull(penguins,species))
  count(penguins,species)
  (152/344)*100

##Island 
levels(pull(penguins,island))
  count(penguins,island)
  (168/344)*100
  (124/344)*100
   (68/344)*100

##Flipper length 
mean(as.numeric(pull(penguins,flipper_length_mm)),na.rm = TRUE)

##Bill length 
mean(as.numeric(pull(penguins,bill_length_mm)),na.rm = TRUE)

##Bill depth 
mean(as.numeric(pull(penguins,bill_depth_mm)),na.rm = TRUE)

##Body mass
mean(as.numeric(pull(penguins,body_mass_g)),na.rm = TRUE)

##Sex
count(penguins,sex)
  (168/344)*100
  (165/344)*100
 
```

This is my scatterplot of bill and flipper length by penguin species! I'm really proud of this because I could barely open RStudio last week. 

```{r making my scatterplot and saving it}
ggplot(penguins, aes(bill_length_mm, flipper_length_mm)) + geom_point(aes(colour = species)) + ggtitle("Penguin Bill and Flipper Length in mm") + labs (y = "Flipper Length (mm)", x = "Bill Length (mm)")

ggsave("hw1_scatterplot.pdf", height = 4, width = 6)

```



