---
title: "Homework 1"
Author: Natalie Boychuk
output: github_document
---

This is my solution to Homework 1. First I am going to load the packages I need 

```{r}
library(tidyverse)
```

## Problem 1
Creating a data frame with the specified elements:

```{r}
prob1_df =
  tibble(
    samp=rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a","b","c","d","e","f","g","h","i","j"),
    factor_vec = factor (c("low","low","low","mod", "mod","mod", "mod", "high","high","high"))
  )
```

Taking the mean of each variable in my data frame. 

```{r attempting to take the mean}
    mean(pull(prob1_df, samp))
    mean(pull(prob1_df, samp_gt_0))
    mean(pull(prob1_df, char_vec))
    mean(pull(prob1_df, factor_vec))
```

I cannot take the mean of the character vector or the factor vector, because R does not recognize these as numbers.

```{r converting logical, char, and factor vectors to numeric}
    as.numeric(pull(prob1_df,samp_gt_0))
    as.numeric(pull(prob1_df,char_vec))
    as.numeric(pull(prob1_df,factor_vec))
```

I can convert the logical and factor vectors to numeric but I can't do the same thing with character vectors. I couldn't take the factor vector as a mean, but if I want to, I can convert this into a numeric vector and then take the mean. I can't do this with a character vector - this may be because R can't find a way to meaningfully assign numbers to characters. 

```{r converting logical vector and multiplying }
    as.numeric(pull(prob1_df,samp_gt_0))*pull(prob1_df,samp)
    as.factor(pull(prob1_df,samp_gt_0))*pull(prob1_df,samp)
    as.numeric(as.factor(pull(prob1_df,samp_gt_0)))*pull(prob1_df,samp)
```



## Problem 2 

