---
title: "Homework 1"
Author: Natalie Boychuk
output: github_document
---

This is my solution to Homework 1. 

_First I am going to load the packages I need._

```{r}
library(tidyverse)
```

## Problem 1
_Then I created a data frame with the specified elements_

```{r}
prob1_df =
  tibble(
    samp=rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a","b","c","d","e","f","g","h","i","j"),
    factor_vec = factor (c("low","low","low","mod", "mod","mod", "mod", "high","high","high"))
  )
```

_I then took the mean of each variable in my data frame._ 

```{r attempting to take the mean}
    mean(pull(prob1_df, samp))
    mean(pull(prob1_df, samp_gt_0))
    mean(pull(prob1_df, char_vec))
    mean(pull(prob1_df, factor_vec))
```

I cannot take the mean of the character vector or the factor vector, because R does not recognize these as numbers.

```{r converting logical, char, and factor vectors to numeric}
    as.numeric(pull(prob1_df,samp_gt_0))
    as.numeric(pull(prob1_df,char_vec))
    as.numeric(pull(prob1_df,factor_vec))
```

I can convert the logical and factor vectors to numeric but I can't do the same thing with character vectors. I couldn't take the factor vector as a mean, but if I want to, I can convert this into a numeric vector and then take the mean. I can't do this with a character vector - this may be because R can't find a way to meaningfully assign numbers to characters. 

```{r converting logical vector and multiplying }
    as.numeric(pull(prob1_df,samp_gt_0))*pull(prob1_df,samp)
    as.factor(pull(prob1_df,samp_gt_0))*pull(prob1_df,samp)
    as.numeric(as.factor(pull(prob1_df,samp_gt_0)))*pull(prob1_df,samp)
```

## Problem 2 
_First, I loaded the penguin dataset_
```{r}
data("penguins", package = "palmerpenguins")
```

The _Penguins_ dataset has `r nrow(penguins)` observations represented by rows and `r ncol(penguins)` variables, which are displayed in the columns. An average penguin in this dataset has a flipper length that is 200.92mm. Their bills are, on average, 43.92mm long and 17.15mm deep. The mean weight of penguins included in this study is 4201.75 grams.

Of the penguins included in this study, 

```{r}
mean(as.numeric
     (pull(penguins,
      flipper_length_mm)), 
        na.rm = TRUE)

mean(as.numeric
     (pull(penguins,
      bill_length_mm)),
        na.rm = TRUE)

mean(as.numeric
     (pull(penguins,
       bill_depth_mm)),
        na.rm = TRUE)

mean(as.numeric
     (pull(penguins,
          body_mass_g)),
            na.rm = TRUE)
```


```{r}

```


```{r}
ggplot(penguins, aes(bill_length_mm, flipper_length_mm)) + geom_point(aes(colour = species)) + ggtitle("Penguin Bill and Flipper Length in mm") + labs (y = "Flipper Length (mm)", x = "Bill Length (mm)")
```

